### 2020-06-23 magic_paper.tex
some restructiing. Also given suggested simpler account of the peak in Lorenz curve.

@@

\begin{theorem}\label{thm:sigmamajor}
    Let $\R = (\F, \O)$ be a theory of magic and suppose the state conversion $\rho \longrightarrow \tau$ is possible within a $\sigma$--fragment for some full-rank free state $\sigma$.
    Then, $\W{\tau} \prec_\sigma \W{\rho}$.
\end{theorem}
\begin{proof}
    Suppose there exists $\E \in \O_\sigma$ such that $\E(\rho) = \tau$.
    Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$.

    Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
\end{proof}

A numerically efficient reformulation of $\bmd$-majorization is provided by Lorenz curves.
Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\bmu \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.

@@

    Expressed explicitly,
    \begin{equation}
		\lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i x + \lc{\rho}{\sigma}(i) - (\bmu^\downarrow)_i x_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
	for all $i=1,\dots,d$ with $x_0 \coloneqq 0$.
\end{definition}
\nick{Move the complicated last equation to appendix?}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\bmu^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.

@@

\subsection{Lorenz curves for magic states in a $\sigma$--fragment}
It is now straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.

@@

@@

We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
	\begin{equation}
		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
	for all $i=1,\dots,d^2$.

\end{proof}
\nick{Perhaps create Lorenz curve appendix and put the proof there as well as how functional form and discretised form of Lorenz curves relate}
We can therefore view mana as one of the features of the Lorenz curve, its maximum.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in all $\sigma$--fragments.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
    \begin{equation}
        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the $\W{\sigma}$--majorization bound
    \begin{equation}
    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
    \end{equation}
    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
\end{proof}

As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
\begin{equation}\label{eq:Skmax}
    \max_{x\in [0,1]}{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^k \right).
\end{equation}
%1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
%\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ]

Consider the noisy Strange state,
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in $\O_\sigma$.
At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
\begin{equation}\label{eq:sdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes k} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
\end{equation}

>>>>

\ddd{[Things we must emphasize:
\begin{enumerate}
\item We can tackle more `physicsy' questions like: how much magic can be distilled via free operations with some given fixed-point structure? E.g. 
\item This allows a diagnostic on the kind of operations needed to do good distillation. I.e. what fixed point structure should they have?
\item We go beyond magic monotones and replace a monotone with a $\sigma$-fragment.
\item We can get both upper and lower bounds on magic distillation.
\end{enumerate}•
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{theorem}\label{thm:sigmamajor}
    Let $\R = (\F, \O)$ be a theory of magic. Then $\rho \longrightarrow \tau$ is possible then  $\W{\tau} \prec_\sigma \W{\rho}$ within a $\sigma$--fragment.
\end{theorem}
\begin{proof}Suppose we can convert $\rho$ into $\tau$ in the magic theory. Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$. Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
\end{proof}
This result can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \le \M(\rho)$ with $W_\tau \prec_\sigma W_\rho$. However the majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- this enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.

This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. This is more involved and we discuss this later in the paper.

\subsection{Majorization computations in a $\sigma$--fragment}
A numerically efficient reformulation of $\bmd$-majorization is provided by Lorenz curves.
Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\bmu \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.

@@

    Expressed explicitly,
    \begin{equation}
		\lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i x + \lc{\rho}{\sigma}(i) - (\bmu^\downarrow)_i x_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
	for all $i=1,\dots,d$ with $x_0 \coloneqq 0$.
\end{definition}
\nick{Move the complicated last equation to appendix?} \ddd{[Yes. Just describe in words, is simpler. the reader with being able to understand how to construct a piecewise linear function.]}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\bmu^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.

@@

It is now straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.

@@

We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
	\begin{equation}
		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
\ddd{[The function is not differentiable at the key points involved. The maximum is obtained when you sum all the non-negative components.]}

\end{proof}
\nick{Perhaps create Lorenz curve appendix and put the proof there as well as how functional form and discretised form of Lorenz curves relate}
\ddd{[This I think is a simpler approach:]}
The Lorenz curve of $L_{\bmx |\bmd}(x)$ is defined by piecewise linear sections sequentially linking the points $\{ (a_k,b_k)\}$ where $a_k = \sum_{i=1}^k x_i$, $ b_k = \sum_{i=1}^k d_i$ and we order the components such that $\tilde{x}_i:=x_i / d_i$ form a non-increasing sequence in $i$.

Now let $k_\star$ be the index of the smallest non-negative number in $(\tilde{x}_i)$, and define 
\begin{align}
a_\star &:= \sum_{i=1}^{k_\star} x_i\\
b_\star &:= \sum_{i=1}^{k_\star} d_i.
\end{align}
It is then clear that $L_{\rho|\sigma}(x)$ attains a maximum value of $a_\star \ge 1$ at the point $x = d_\star$.

Note that since $\bmd \ge \mathbf{0}$, for $i > k_\star$ we have that $x_i \le 0$, independent of the particular $\bmd$ we use. Therefore the value of $a_\star$ is independent of the particular fragment, with only the location of the maximum ($x=b_\star$) varying from fragment to fragment. \ddd{[This method is tidier.]}

We can therefore view mana as one of the features of the Lorenz curve, its maximum.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in all $\sigma$--fragments.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
    \begin{equation}
        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the $\W{\sigma}$--majorization bound
    \begin{equation}
    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
    \end{equation}
    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
\end{proof}

As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, and for the $k$-copy state we have that
\begin{equation}\label{eq:Skmax}
    \max_x{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^k \right),
\end{equation}
independent of the particular $\sigma$--fragment. \ddd{[We should also give for what value of $x$ this maximum occurs.]} 
%1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
%\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ]

\subsection{Distilling out magic in a fragment}
Consider, as an example, the problem of purifying out magic from a noisy state of the form
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in $\O_\sigma$.
At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
\begin{equation}\label{eq:sdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes k} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
\end{equation}

@@
